---
title: "Allie's Blog Page"
output: html_document

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Qualtrics
#### March 8, 2020
I am an undergraduate research assistant with the Cultural Heritage and Racial Identity lab. We're starting a new study that includes a questionnaire on Qualtrics. One of my tasks as part of the lab is to input and formulate a questionnaire. I've been learning a lot about how Qualtrics works and what formatting is best for participants. For example, it is better to format multiple choice answers vertically instead of horizontally because that way is easiest for reading on mobile devices.


### R graphing
#### March 3, 2020
In my STAT 385 class I've been learning how to make a lot of different graphs using R. Here are some examples of my work:
```{r}
plot(Sepal.Width~Sepal.Length, data = iris, 
     main = "Iris Sepal Length vs. Sepal Width by Species",
     xlab = "Sepal Length", ylab = "Sepal Width",
     col= c("green", "red", "blue")[(iris$Species)],
     pch = 19)
box()
grid()
```

```{r}
hist(x = iris$Sepal.Length, main = "Histogram of Sepal Length", xlab = "Sepal Length",
     breaks = 15, border = "dodgerblue", probability = TRUE,
     ylim = c(0, 0.65), xlim = c(4, 8.2))
abline(v = mean(iris$Sepal.Length), col = "red")
text(x = mean(iris$Sepal.Length) + 0.3, y = 0.6, labels = "x = 5.843", col = "red")
box()
grid()
```

```{r}
hist(x = faithful$eruptions, 
     main = "Histogram of Old Faithful Geyser Eruption Time",
     xlab = "Eruption Time (mins)", ylab = "Density", 
     probability = TRUE, 
     breaks = 20, border = "purple")
lines(x = density(faithful$eruptions), col = "orange")
box()
grid()
```

```{r}
par(mfrow = c(1,2))
hist(x = faithful$waiting, 
     main = "Histogram of Old Faithful Waiting Time",
     xlab = "Waiting Time (mins)", ylab = "Density", 
     probability = TRUE, 
     breaks = 10, border = "blue")
box()
grid()
plot(eruptions~waiting, data = faithful,
     main = "Waiting Time vs. Eruption Time",
     xlab = "Waiting Time (mins)", ylab = "Eruption Time (mins)", 
     col = "blue", pch = 16)
box()
grid()
```
